Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-04-10 WSSSPE4_report/WSSSPE4_report.tex
resolving comments from Dan

    \item \textbf{Mistral Contrastin, Matthew Danish,
    Dominic Orchard\textsuperscript{\textasteriskcentered}, and
    Andrew Rice: \emph{Supporting software sustainability with
    lightweight specifications}}~\cite{Contrastin:2016ws}.
    This talk introduced the tool CamFort for verifying Fortran code based on
    lightweight specifications, which aid in software maintainability and reuse
    through high-level indications of programmer intent.
    Currently, CamFort supports specification (and
    verification) of units and stencil operations. Plans for future specifications
    include automatic test generation based on user-supplied properties, dependency
    specifications, and software contracts to check (e.g.) expected value ranges
    and program behavior.

@@

    \item \textbf{Lukas Breitwieser\textsuperscript{\textasteriskcentered},
    Roman Bauer, Alberto Di Meglio, Leonard Johard,
    Marcus Kaiser, Marco Manca, Manuel Mazzara, Fons Rademakers,
    Max Talanov: \textit{The BioDynaMo Project}}~\cite{Bauer:2016ws}.
    Breitwieser described the BioDynaMo project, a large-scale platform for
    biological simulations that provides access to computational resources while
    hiding the complexity of distributed computing. It also promotes computational
    reproducibility through shared open-access data. The project began as a
    modernization initiative porting an existing simulation software, Cx3D, from
    Java to C++, but also incorporated many modern software engineering practices
    such as hosting and version control on GitHub, automated tests and continuous
    integration via Travis-CI, code coverage reports, and an automated build system.
    In addition, over 1000 students participated in development via the Intel
    Modern Code Developer Challenge competition---the winner achieved a
    performance speedup of 320 times. The project plans to continue improving
    the development process with (e.g.) static code checkers and Git commit hooks,
    continued architecture redesign, and verification.

>>>>

    \item \textbf{Mistral Contrastin, Matthew Danish,
    Dominic Orchard\textsuperscript{\textasteriskcentered}, and
    Andrew Rice: \emph{Supporting software sustainability with
    lightweight specifications}}~\cite{Contrastin:2016ws}.
    This talk introduced the tool CamFort for verifying Fortran code based on
    lightweight specifications, which aid in software maintainability and reuse
    through high-level indications of programmer intent.
    Currently, CamFort supports specification (and
    verification) of units and stencil operations. Plans for future specifications
    include automatic test generation based on user-supplied properties, dependency
    specifications, and software contracts to check, e.g., expected value ranges
    and program behavior.

@@

    \item \textbf{Lukas Breitwieser\textsuperscript{\textasteriskcentered},
    Roman Bauer, Alberto Di Meglio, Leonard Johard,
    Marcus Kaiser, Marco Manca, Manuel Mazzara, Fons Rademakers,
    Max Talanov: \textit{The BioDynaMo Project}}~\cite{Bauer:2016ws}.
    Breitwieser described the BioDynaMo project, a large-scale platform for
    biological simulations that provides access to computational resources while
    hiding the complexity of distributed computing. It also promotes computational
    reproducibility through shared open-access data. The project began as a
    modernization initiative porting an existing simulation software, Cx3D, from
    Java to C++, but also incorporated many modern software engineering practices
    such as hosting and version control on GitHub, automated tests and continuous
    integration via Travis-CI, code coverage reports, and an automated build system.
    In addition, over 1000 students participated in development via the Intel
    Modern Code Developer Challenge competition---the winner achieved a
    performance speedup of 320 times. The project plans to continue improving
    the development process with, e.g., static code checkers and Git commit hooks,
    continued architecture redesign, and verification.
